BERT Model Compression and Weight Sharing

### 2019-05-11 paper/paper.tex
Fix duplicate figure label warning in paper.tex
Setting up notation

@@

@@

\begin{itemize}
\item How do you plan on training your parameters / inferring the
  states of your latent variables (MLE / MAP / Backprop / VI / EM / BP / ...)

@@

\item What is the explicit method / algorithm that you derive for learning these parameters?
\end{itemize}

@@

\begin{table}
  \centering
  \missingfigure[figheight=5cm]{}
  \caption{Secondary table or figure in results section.}
  \label{fig:mainres}
\end{table}

>>>>

\newcommand{\bert}{\operatorname{BERT}}
\newcommand{\distortion}{\operatorname{Distortion}}
\newcommand{\prune}{\operatorname{Prune}}
\newcommand{\diffprune}{\operatorname{DiffPrune}}

\newcommand{\btheta}{{\bm{\theta}}}
\newcommand{\bphi}{{\bm{\phi}}}
\newcommand{\bpsi}{{\bm{\psi}}}

@@

We first set up some notation. Let $F_\btheta = G_\bpsi \circ \bert_\bphi$ be a
transformed model where
$\btheta = (\bphi, \bpsi)$ be parameters of the subparts of the model.
$\bert_\bphi$ is a BERT model where the pretrained weights are $\bphi_0 = 
(\bphi_0^i)_{i=1}^n$, and
$G_\bpsi$ is additional layers for fine-tuning BERT, parameterized by $\bpsi$.
We decompose the subparts of the model into layers: \begin{align*}
\bert_\bphi &= f_{n}^{\bphi_n} \circ \cdots \circ f_1^{\bphi_1} \\
G_\bpsi &= g_{m}^{\bpsi_m} \circ \cdots \circ g_1^{\bpsi_1}.
\end{align*}

\subsection{DeepTwist-based Weight Distortions}

@@

\begin{comment}
\begin{itemize}
\item How do you plan on training your parameters / inferring the
  states of your latent variables (MLE / MAP / Backprop / VI / EM / BP / ...)

@@

\item What is the explicit method / algorithm that you derive for learning these parameters?
\end{itemize}
\end{comment}

@@

% \begin{table}
%   \centering
%   \missingfigure[figheight=5cm]{}
%   \caption{Secondary table or figure in results section.}
%   \label{fig:mainres}
% \end{table}
